\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
changed the L2 diagram, added some texts and a ref to appendix

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata. \textblue{Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs}. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.

>>>>

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata. \textblue{Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs}. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.\textblue{ Figure~\ref{fig:lissyl2} illustrates a high level overview of how traders interact with \cm on Arbitrum (\ie  bridge ETH into Arbitrum chain, execute functions on \cm \etc) in Appendix~\ref{app:rollup}.}
